Detecting TravisCI Misconfiguration

### 2016-08-25 Travis/main.tex
actually a pretty nice sketch of temporal learning

\usepackage{amsmath}
\usepackage{todonotes}
\usepackage{graphicx}\usepackage{color}
\usepackage{csquotes}

@@

>>>>

\usepackage{amsmath}
%\usepackage{todonotes}
\usepackage{graphicx}\usepackage{color}
% \usepackage{csquotes}

@@

\subsection{Learning from Temporal properties}

An intersting extension to ConfigC on a theortical side is to look at the temporal relations between commits.
The key observation is that with each commit that changes the build status, we can learn highly localized information about our model.

The first step is to build an intermediate representation of the data we will learn.
For the sake of efficiency, this data must be structured as a shallow tree.
While the travis.yml file can be taken verbatim, we must use a simplification of the program code.
Since we are only intrested in the parts of the program effecting build status, we should extract the imported libraries as a list.
We will call this summary $S_t$, a simplified representation of the program which contains only the information relevant to the learning process.
The subscript is a tag based on the ordered commit history.
To handle branches, add a superscript to indicate the branch, and restart the counter on a branch - merging should be handled easily (not exactly sure how yet).

From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the model.
These possible rules must be given by the user.
In \cite{CAV}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.

We will denote the build status of $S_t$ with $B(S_t)$.
In this application, we consider only the passing and erroring build status, denoted $P$, and $E$ respectivly.
All status that are not \verb|error|, as defined by the Travis API, will be included as passing.
For brevity, we denote sequences of build statuses with the following notation:

$S(P_t)=P \land S(P_{t+1})=E \implies S(P_{t,t+1}) = PE$

We know that if a build is passing, then there must not exist any errors.
That is, the model must not contain any rules which are breaking.
Note we are not, however, garunteed that any rules from a passing commit are necessary.

$S(P_t)=P \implies \forall r \in M(P_t), r \notin Br$

The key insight is that when we commit a break, we can localize the error to one of the lines that changed.
Either we removed something that was necessary, or added something that was breaking.
We use an inclusive disjunction, since a erroring commit can break multiple things at once.
Expressed formally, where ($\setminus$ is the set difference), that is:

\begin{align*}
  S(P_{t,t+1}) = PE \implies \\
  \exists r \in (M(P_{t})\ \setminus M(P_{t+1})), r \in Nec\ \lor \\
  \exists r \in (M(P_{t+1}) \setminus M(P_{t})), r \in Br
\end{align*}

We then can combine all these formulas with conjunctions and send it to an SMT solver and magically get an answer.
While exstential set operations can be expensive in general for an SMT solver, in our application this is not the case.
Because these sets will be small thanks to the practice of making incremental commits when using source control, these operations will be fairly cheap.
In fact, the above implication generalizes to $P_{t,t+n}$, but for efficency we must require that $M(P_{t})\ \setminus M(P_{t+n})$ is managably small.
The definition of small here remains to be experimentally determined.

In fact, I think this approach should work generally for any ML problem where we have an oracle (e.g. neural nets, SVMs), but would like justifications for the classification.
Using this as a second stage of a machine learning algorithm might be really interesting.
